---
title: "Recreation"
author: "Alene Onion"
date: "January 3, 2019"
output:  
  html_document:
    toc: true
    toc_depth: 6
    toc_float: true
---

##Swimming  

Components:  
```{r, echo=FALSE,results='asis'}
short<-c('DB','Clarity','Control','ChlA','sTOX','sHABs','TOX','BGA','CT','HABn','nutrients')
definition<-c('number of days beaches were closed',
              'Percentage of clarity observations since 2011 (or 2018) less than 1.21',
              'Control measures',
              'Percentage of Chl A readings since 2011 (or 2018) exceeded the standard (>10 for recreation)',
              'Count of shore samples >4 since 2011 (or 2018)',
              'Count of shoreline habs that have FP-BGChl reading over 25 since 2011 (or 2018)',
              'Count of surface samples >4 since 2011 (or 2018)',
              'Surface readings of FP-BGChl over 25 since 2011 (or 2018)',
              'Trend score for clarity or Chla (whichever is max) since sampling began',
              'Any HAB notification',
              'Percentage of phosphorus samples that exceeded 0.02 since 2011')
components<-data.frame(short,definition)
knitr::kable(components)
rm(list=c('short','definition','components'))
```

Additional definitions/Notes:  

* Trend score = RegScore x Pscore x SIGN
    + RegScore = 0 (if n<5 | r2<0.3), 1 (if 0.03<=r2<0.5), 2 (if r2>=0.5)  
    + PScore = 0 (if n<5 | p>0.05), 1 (if 0.01<p<=0.05), 2 (if p<=0.01)
    + SIGN = 0 (if slope=0), 1 (if slope is +), -1 (if slope is -)
  
Components for av year: 

```{r, echo=FALSE,results='asis'}
score<-c(0,1.025,1.1,1.2,1.3,1.4,1.5,2.025,2.05,2.1,2.2,2.3,2.4,2.5,2.6,2.8,2.9,3.05,3.6,3.7,3.8,3.9)
DB<-c('','','','','','','','','','','','','','','','','2.9','','','','','>10')
Clarity<-c('','','','','','','','','','','','','','','','>10','','','','','>50','')
Control<-c('no','','','','','','','','','','','','','','','','','','','!no','','')
ChlA<-c('','','','','','','','','','','','','','','>10','','','','>50','','','')
sTOX<-c('','','','','','','1','','','','','','','>1','','','','','','','','')
sHABs<-c('','','','','','1','','','','','','','>1','','','','','','','','','')
TOX<-c('','','','','1','','','','','','','>1','','','','','','','','','','')
BGA<-c('','','','1','','','','','','','>1','','','','','','','','','','','')
CT<-c('','','2','','','','','','','4','','','','','','','','','','','','')
HABn<-c('no','','','','','','','','1','','','','','','','','','>1','','','','')
nutrients<-c('','>10','','','','','','10<x<50','','','','','','','','','','','','','','')
recr<-data.frame(score,DB,Clarity,Control,ChlA,sTOX,sHABs,TOX,BGA,CT,HABn,nutrients)
knitr::kable(recr)
rm(list=c('recr','score','DB','Clarity','Control','ChlA','sTOX','sHABs','TOX','BGA','CT','HABn','nutrients'))
```	

Components for 2018:  

```{r, echo=FALSE,results='asis'}
score<-c(0,1.2,1.3,1.4,1.5,1.6,1.7,2.1,2.2,2.3,2.4,2.5,2.6,2.7,2.8,2.9,3.4,3.8,3.9)
Clarity<-c('','','','','','','','','','','','','','','','>10','','','>50')
ChlA<-c('','','','','','','','','','','','','','','>10','','','>50','')
sTOX<-c('','','','','','','1','','','','','','','>1','','','','','')
sHABs<-c('','','','','','1','','','','','','','>1','','','','','','')
TOX<-c('','','','','1','','','','','','','>1','','','','','','','')
BGA<-c('','','1','','','','','','','>1','','','','','','','','','')
HABn<-c('','','','','','','','','','','1','','','','','','>1','','')
nutrients<-c('','>10','','','','','','','>50','','','','','','','','','','')
recr<-data.frame(score,Clarity,ChlA,sTOX,sHABs,TOX,BGA,HABn,nutrients)
knitr::kable(recr)
rm(list=c('recr','score','Clarity','ChlA','sTOX','sHABs','TOX','BGA','HABn','nutrients'))
```	

Total Score for Swimming  
```{r, echo=FALSE,results='asis'}
score<-c(2,3,4,5,6)
translation<-c('Not Known','Supported/Good','Threatened/Fair','Stressed/Poor','Impaired')
avYear<-c('','0>max(RECR)<1','max(RECR)>1','max(RECR)>2','max(RECR)>3')
y2018<-c('','0>max(RECR18)<1','max(RECR18)=1','max(RECR18)=2','max(RECR18)=3')
SwimScore<-data.frame(score,translation,avYear,y2018)
knitr::kable(SwimScore)
rm(list=c('score','avYear','SwimScore','translation','y2018'))
```	

Primary Issue  
The primary issue is simply the highest scoring component in the list  
